Modal Abstractions for Virtualizing Memory Addresses

### 2023-03-01 programlogic.tex
+

Being inspired by what hybrid logic \ref{} calls a satisfaction operator, which evaluates the truth of a predicate in a named alternative state (here, address space), we give a modal definition describing the truth of assertions for the resources inside the address space, $[r]P$ indicating that $P$ holds in the virtual address space rooted at $r$. While doing so, we explain what a modal resource context is, and how it interacts with the ambient logic, i.e. separation logic.
\paragraph{Modal Resource Context}
\label{sec:resourcecontext}
When we pick up a certain contingency, which is \textit{"a certain virtual-pointsto facts whose validity is indexed by the root address of an address space"}for address space modality, we, in fact, make our choice around some logical resources for which we care about reasoning, which is virtual pointsto relation shown in Figure \ref{fig:virtualpointstosharing}. In other words, our modality definition is the logical virtual pointsto resources: introduction/elimination of logical virtual pointsto resources are the ones essential to the reasoning capabilities the address space modality provides, i.e. validity of virtual addresses under/out of modality -- resources under/out of \textit{modal resource context}.  
\paragraph{Interaction}
\label{sec:interaction}

>>>>

Being inspired by what hybrid logic \ref{} calls a satisfaction operator, which evaluates the truth of a predicate in a named alternative state (here, address space), we give a modal definition describing the truth of assertions for the resources inside the address space, $[r]P$ indicating that $P$ holds in the virtual address space rooted at $r$. While doing so, we explain what a modal resource context is, and how it interacts with the ambient logic, i.e. separation logic.
\paragraph{Modal Resource Context}
\label{sec:resourcecontext}
When we pick up a certain contingency, which is \textit{"a certain virtual-pointsto facts whose validity is indexed by the root address of an address space"}for address space modality, we, in fact, make our choice around some logical resources for which we care about reasoning, which is virtual pointsto relation shown in Figure \ref{fig:virtualpointstosharing}. In other words, our modality definition is the logical virtual pointsto resources: introduction/elimination of logical virtual pointsto resources are the ones essential to the reasoning capabilities the address space modality provides, i.e. validity of virtual addresses under/out of modality -- resources under/out of \textit{modal resource context}.

The choice modal context itself already exhibits itself as a reasoning principle (Figure \ref{fig:modalcontextinvariance}) in which we can intro/eliminate any resource that is not virtual pointsto into/from modal context without dischargin any obligation. We can use this entailment for  \todo[inline,color=red]{Ask Colin}.
\begin{figure}
  \[
  \begin{array}{l}
\hbox{(\TirNameStyle{ModalContextInvariance})} \qquad
 [r](Q \star \ell \mapsto_{\textsf{p}} \vpage)  \;\vdash [r](Q) \star \ell \mapsto_{\textsf{p}} \vpage 
  \end{array}
  \]
\caption{Modal Context Invariance}
\Description{Modal Context Invariance}
\label{fig:modalcontextinvariance}
\end{figure}
\begin{remark}[The Choice of Modal Context as a Pattern of Verification]
  By choosing the contingency and the modal contex, we simply introduce 
  \begin{enumerate}
  \item the pattern of what the essential abstraction (e.g. address spaces) we care about to do verification is
  \item how a modal context (e.g. a address-space modality), logically, draws the attention to the certain facts in the interest of reasoning (e.g. virtual pointsto relations in the current address-space)
  \item and, offloads the burden of individual bookkeeping of these facts being interesting under different context (e.g. virtual pointsto relations in other address-spaces) via utilizing the \textit{summarization} aspect of the contingency it represents (e.g. other virtual pointsto relations are valid under other certain address-space page-table root addresseses).  
  \end{enumerate}
\end{remark}
\paragraph{Interaction}
\label{sec:interaction}
After defining the modal context, we can now use introduction/elimination of a resource into/from a modal context for the sake of real low-level systems verification. For example, we can extend the modal context with some new virtual address mapping after backing them with new pages...

After defining the mod 
This rule captures the notion that switching address spaces pulls information out of one modality into the \textit{“current view”} of memory, and leaves other assertions true relative to the previous address
space.
